---
#citeproc: no
graphics: yes
name: JooYoung
surname: Seo
position: "Ph.D. Candidate (ABD)"
address: "Learning, Design, and Technology, 301 Keller Building, University Park, PA 16802, USA"
phone: "+1 814-777-5825"
www: jooyoungseo.com
email: "jooyoung@psu.edu"
twitter: sjystu
github: jooyoungseo
linkedin: jooyoungseo
aboutme: |
  I am a learning scientist, software engineer, and accessibility professional.
date: "`r format(Sys.time(), '%B %Y')`"
csl: "csl/apa6-cv.csl"
nocite: "@*"
#output:
#  vitae::moderncv:
#    theme: classic
#    fig_caption: yes
#    keep_tex: yes
#    pandoc_args:
#      - --lua-filter="lua/multiple-bibliographies.lua"
#      - !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_replace_ampersands_filter(rmdfiltr::add_citeproc_filter(args = NULL)))
#      - !expr system.file("resources", "lua", "multiple-bibliographies.lua", package = "vitae")
bibliography_selected: "bib/selected.bib"
bibliography_journals: "bib/journal.bib"
bibliography_proceedings: "bib/proceedings.bib"
bibliography_working_paper: "bib/working_paper.bib"
bibliography_R_packages: "bib/R-packages.bib"
bibliography_github_projects: "bib/github.bib"
---

```{r setup, include=FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "",
           cite.style = "alphabetic",
           style = "markdown",
#           hyperlink = FALSE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(ezpickr)
```

# Research Areas

 * Inclusive Makerspaces
 * Accessible STEM Learning
 * Computational Thinking for Learners with dis/ABILITIES
 * Inclusive CSCL (Computer-Supported Collaborative Learning)
 * Accessibility
 * Universal Design
 * Assistive Technology

# Primary Research Methods

 * Supervised/Unsupervied Machine Learning-Based Text Mining 
 * Computational Linguistics
 * Data Science-Based Reproducible Research
 * Quantitative Ethnography

# Education

```{r education}
ezpickr::pick("data/education.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Certificate

```{r certificate}
ezpickr::pick("data/certificate.xlsx") %>%
  vitae::detailed_entries(what, when, with, where)
```

# Research Experience

```{r research-experience}
ezpickr::pick("data/research-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Teaching Experience

```{r teaching-experience}
ezpickr::pick("data/teaching-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Working Experience

```{r working-experience}
ezpickr::pick("data/working-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Awards and Honors

```{r award}
ezpickr::pick("data/award.xlsx") %>%
#  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where)
```

# Grants

```{r grant}
ezpickr::pick("data/grant.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Publications

## Selected Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_selected}
:::
\endgroup

## Refereed Journal Papers

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_journals}
:::
\endgroup

## Papers in Refereed Conference Proceedings

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_proceedings}
:::
\endgroup

## Working Papers under Revision or Review

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_working_paper}
:::
\endgroup

# Software Developments and Publications

## Peer-Reviewed Data Mining Packages

```{r R-package, echo = FALSE, cache = FALSE, eval=T}
#knitr::write_bib(c('ezpickr', 'mboxr', 'youtubecaption'), "bib/R-packages.bib")
#R_package <- suppressMessages(RefManageR::ReadBib("bib/R_packages.bib", check = FALSE))
#RefManageR:::print.BibEntry(R_package)
vitae::bibliography_entries("bib/R-packages.bib")
```

<!-- \begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_R_packages}
:::
\endgroup -->

## Open-Source Project on GitHub

```{r github, echo = FALSE, cache = FALSE, eval=T}
#knitr::write_bib(c('tactileR', 'ezviewr', 'jladown'), "bib/github.bib")
#github <- suppressMessages(RefManageR::ReadBib("bib/github.bib", check = FALSE))
#RefManageR:::print.BibEntry(github)
vitae::bibliography_entries("bib/github.bib")
```

<!-- \begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_github_projects}
:::
\endgroup -->

## Officially Contributing R Packages

* My name has been officially listed as a contributor for the following refereed open-source packages:

```{r contribute}
ezpickr::pick("data/contribute.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Presentations

## Peer-Reviewed Conference Posters and Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("data/poster.txt")`

\endgroup

## Invited Guest Lectures

```{r talk}
ezpickr::pick("data/talk.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why, .protect = TRUE)
```

# Service

```{r service}
ezpickr::pick("data/service.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Skills

## Programming Languages

* Data Mining: R, Python, and SQL (as advanced level as being able to develop and release packages and libraries).
* Web Programming: HTML/CSS/JavaScripts/PHP (as advanced level as being able to develop and maintain accessible web modules and application).
* Operating System: Unix/Linux (as advanced level as being able to develop and maintain system-level Shell scripts for server and database programs).
* Compile Languages: C/C++ and Java (as basic level as being able to review source codes and develop simple modules).
* Others: Git, Docker, Travis CI, LaTeX, Markdown, Pandoc, Lua, and Quorum.

## Languages

* English: professional fluency in reading, writing, listening and speaking.
* Korean: native fluency in reading, writing, listening and speaking.
* Japanese: basic fluency in reading, writing, listening and speaking.

## Software

* Statistical Software: R and Python (professional level), SPSS/SAS, MiniTab, and Stata.
* Office Programs: Microsoft Office and Google Suites.
* Learning Management System: Canvas and Angel.
* General Web Content Management: WordPress, Drupal, and Hugo.

# Current Memberships

  * Member, International Society of the Learning Sciences (ISLS)
  * Member, Association for Computing Machinery (ACM)
  * Member, American Educational Research Association (AERA)
  * Member, Association for Educational Communications and Technology (AECT)
  * Member, International Association of Accessibility Professionals (IAAP)
