---
title: JooYoung Seo's Curriculum Vitae
graphics: yes
name: JooYoung
surname: Seo
headcolor: 414141
#qualifications: 
position: "Ph.D."
pronouns: he/him/his
address: "614 E. Daniel St. | Room 5158, Champaign, IL 61820"
phone: "+1 217-333-2671"
www: jooyoungseo.github.io
email: "jseo1005@illinois.edu"
twitter: seo_jooyoung
github: jooyoungseo
linkedin: jooyoungseo
aboutme: |
  I am a learning scientist, data-science/software developer, and internationally certified accessibility professional.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa7-cv-jy-edition.csl"
header-includes:
  # allow URLs to break at any character
  - \usepackage{xurl}
  # - \usepackage{fancyhdr}
  # - \pagestyle{fancy}
  # - \fancyhf{}
  # - \fancyhead[R]{\thepage}
knit: (function(input, ...) {lapply(bookdown::render_book(input, output_file = "docs/JooYoung_Seo_CV", output_format = "all", envir = globalenv(), ...), browseURL)})
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(vroom)
```

<!--chapter:end:index.Rmd-->

# Education

```{r education}
vroom::vroom("data/education.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:education.Rmd-->

# Professional Appointment

```{r appointment}
vroom::vroom("data/appointment.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:appointment.Rmd-->


# Grants

<!-- ```{r grant, eval = FALSE}
vroom::vroom("data/grant.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
``` -->

## Awarded Grants

- "Beyond Visuals: Improving Accessibility of Data Curation and Multi-Modal Representations for People of all Abilities through Reproducible Workflows," PI, Institute of Museum and Library Services (IMLS) Laura Bush 21st Century Librarian Program, Grant #RE-254891-OLS-23, $649,921, Aug 2023 - July 2026 (ongoing).

- "Promoting Computational Thinking Skills for Blind and Visually Impaired Teens through Accessible Library Makerspaces," PI, Institute of Museum and Library Services (IMLS) National Leadership Grants, Grant #LG-252360-OLS-22, $498,638, Aug 2022 - May 2025 (ongoing).

- "Inclusive Data Science: Fostering Accessibility and Reproducibility with Multimodal Learning Strategies," PI, Teach Access Faculty Grants, Tier 3, $5,000, May 2023 - May 2024 (ongoing).

- "Improving Accessible Reproducibility for Data Science Publishing System," PI, Posit PBC (unrestricted gift), $54,327, May 2022 - Present (ongoing).

- "Co-designing an Alexa-Based Conversational mHealth System with Visually Impaired People to Promote Physical Activities," Co-PI, Center on Health, Aging, and Disability’s (CHAD) Pilot Grant Program at the University of Illinois at Urbana-Champaign, $29,866, 2023-2024 (ongoing).

- "Category I: Crossing the Divide Between Today's Practice and Tomorrow's Science," Senior Personnel, National Science Foundation (NSF), Grant #2005572, $10,000,000.00, Oct 2021 - Sept 30, 2026 (.5 FTE academic year) (ongoing).

- "Insight without Sight: Enhancing Data Literacy through Multimodal Data Science Education - Smith-Kettlewell Summer Institute," Subaward PI, Rehabilitation Engineering Research Centers (RERC) Program: RERC on Blindness and Low Vision, National Institute on Disability, Independent Living, and Rehabilitation Research (NIDILRR), Grant #90REGE0018-01-00, $11,975, July 17, 2023 - August 11, 2023 (completed).

- "Data Accessibilization: Making Data Science Education Accessible for Blind Learners," PI, Wallace Foundation, Emerging Scholars Program, International Society of the Learning Sciences, $10,000, Jan 2022 - Dec 2022 (completed).

## Under-Review Grants

- "Collaborative Research: SpatioTemporal Representations for Information and Data Equity: An Interactive AudioTactile System for BVI Data Scientists," PI (at UIUC), National Science Foundation (NSF), Workplace Equity for Persons with Disabilities in STEM and STEM Education (nsf23593), $573,548 (for UIUC) out of $1,499,917 total, July 2024 - June 2028 (under review).

<!-- ## Unawarded Projects

- "Multimodal Data Representations Using Generative AI with, by, and for Blind and Low-Vision People," PI, Google Research: Award for Inclusion Research Program, $60,000, August 2023 - July 2024 (unawarded).

- "Developing an Accessible Mobile Food Tracking Application With and For Blind People," Co-PI, National Institute on Disability, Independent Living, and Rehabilitation Research, HHS-2023-ACL-NIDILRR-IFDV-0000, $600,000 (UIUC: $180,000), 2023-2026 (unawarded).

- "Whole Tale Accessibility Project," Co-PI, The Sloan Foundation, Submitted for Aug 2022 - Aug 2023, $225,000 (unawarded).

- "Understanding the Sleep Patterns of Blind Populations Using Self-Tracking Technologies - What is It Like and How can We Support It?", Co-PI, The Center on Health, Aging, and Disability, College of Applied Health Sciences, Submitted for July 2022 - December 2023, $30,000 (unawarded). -->

<!--chapter:end:grant.Rmd-->

# Publications

* The following notations only apply to September 2021 and after.

`#`: derived from the candidate’s thesis.

`*`: publication that has undergone stringent editorial review by peers.

`+`: publication that was invited and carries special prestige and recognition.

<!-- # Selected Publications -->
<!--  -->
<!-- ::: {#refs_selected} -->
<!-- ::: -->

## Refereed Journal Papers

```{r}
vitae::bibliography_entries("bib/journal.bib")
# arrange(desc(row_number())) %>%
# relocate(annote)
```

## Papers in Refereed Conference Proceedings

```{r}
bibliography_entries("bib/proceedings.bib")
```

## Book Chapters

```{r}
bibliography_entries("bib/book.bib")
```

<!--chapter:end:publication.Rmd-->


## Publications in Healthcare

```{r}
bibliography_entries("bib/healthcare.bib")
```

## Working Papers under Revision or Review

```{r}
bibliography_entries("bib/working_paper.bib")
```

<!--chapter:end:healthcare.Rmd-->

# Conference Presentations and Invited Talks

`r knitr::knit_child("data/poster_short.txt")`

<!-- ## Invited Guest Lectures -->
<!-- ```{r talk}
vroom::vroom("data/talk.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why, .protect = TRUE)
``` -->

<!--chapter:end:presentation.Rmd-->

# Media Coverage

```{r}
bibliography_entries("bib/media_coverage.bib")
```

<!--chapter:end:media_coverage.Rmd-->

# Software Developments and Publications

## Data Science Packages in Comprehensive R Archive Network (CRAN)

<!-- ```{r R-package, echo = FALSE, cache = FALSE, eval = FALSE}
knitr::write_bib(c("ezpickr", "mboxr", "youtubecaption"), "bib/R_packages.bib")
# R_package <- suppressMessages(RefManageR::ReadBib("bib/R_packages.bib", check = FALSE))
# RefManageR:::print.BibEntry(R_package)
#### vitae::bibliography_entries("bib/R_packages.bib")
``` -->

```{r}
bibliography_entries("bib/R_packages.bib")
```

\newpage

## Open-Source Project on GitHub

<!-- ```{r github, echo = FALSE, cache = FALSE, eval=T}
# knitr::write_bib(c('tactileR', 'ezviewr', 'jladown', 'edmdown'), "bib/github.bib")
# github <- suppressMessages(RefManageR::ReadBib("bib/github.bib", check = FALSE))
# RefManageR:::print.BibEntry(github)
#### vitae::bibliography_entries("bib/github.bib")
``` -->

```{r}
bibliography_entries("bib/github.bib")
```

## Officially Code_Contributing R Packages

* [My GitHub pull requests](https://github.com/pulls?q=is%3Apr+author%3Ajooyoungseo+archived%3Afalse+is%3Aclosed) have been peer-reviewed and merged for active data science R packages:

```{r contribute}
# knitr::write_bib(c('bookdown', 'distill', 'BrailleR', 'wordcountaddin'), "bib/contribute.bib")
vroom::vroom("data/contribute.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:software_dev.Rmd-->

# Teaching Experience
<!-- ```{r teaching-experience}
vroom::vroom("data/teaching-experience.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
``` -->

* IS 407: Introduction to Data Science (spring 2022-present).

* IS 569: Internship (spring 2022). *Advised Ankita Khiratkar (MS IM)*.

* IS 589: Independent Study (spring 2022). *Advised Chetna Beri (MS IM)*.

* INFO 399: Individual Study (spring 2022). *Advised Leo Zhang (CS undergrad --> Currently, Master's student at UCLA Data Science dept)*.

* IS 389: Independent Study (spring 2022). *Advised Miso Kim (BS IS)*.

* IS 226: Introduction to Human-Computer Interaction (fall 2021). *Co-teaching with Dr. Yang Wang*.

* Served as an annual review committee member for iSchool Ph.d. student Smirity Kaushik (advisor Dr. Yang Wang) (spring 2022).

* Served as a field exam committee member for iSchool Ph.D. candidate Jaihyun Park (advisor Dr. Ryan Cordell) (spring 2022).

<!--chapter:end:teaching_exp.Rmd-->

# Awards and Honors

```{r award}
vroom::vroom("data/award.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:award.Rmd-->

# Service

```{r service}
vroom::vroom("data/service.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:service.Rmd-->

# Current Memberships

  * International Society of the Learning Sciences (ISLS)
  * Association for Computing Machinery (ACM)
  * American Statistical Association (ASA)
  * International Society for Quantitative Ethnography (ISQE)
  * International Association of Accessibility Professionals (IAAP)
  * International Educational Data Mining Society (IEDMS)
  

<!--chapter:end:membership.Rmd-->

