---
#citeproc: no
graphics: yes
name: JooYoung
surname: Seo
#headcolor: 414141
#qualifications: 
position: "RStudio Intern for Summer 2020; Ph.D. Candidate (ABD)"
address: "Learning, Design, and Technology, 301 Keller Building, University Park, PA 16802, USA"
phone: "+1 814-777-5825"
www: jooyoungseo.com
email: "jooyoung@psu.edu"
twitter: sjystu
github: jooyoungseo
linkedin: jooyoungseo
aboutme: |
  I am a learning scientist, software engineer, and internationally-certified accessibility professional.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "../csl/apa7-cv.csl"
nocite: "@*"
knit: bookdown::render_book
bibliography_selected: "../bib/selected.bib"
bibliography_journals: "../bib/journal.bib"
bibliography_proceedings: "../bib/proceedings.bib"
bibliography_healthcare: "../bib/healthcare.bib"
bibliography_working_paper: "../bib/working_paper.bib"
bibliography_R_packages: "../bib/R_packages.bib"
bibliography_github_projects: "../bib/github.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "",
           cite.style = "alphabetic",
           style = "markdown",
#           hyperlink = FALSE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(ezpickr)
```

# Education

```{r education}
ezpickr::pick("../data/education.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Certificates

```{r certificate}
ezpickr::pick("../data/certificate.xlsx") %>%
  vitae::detailed_entries(what, when, with, where)
```

# Working Experience

```{r working-experience}
ezpickr::pick("../data/working-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Research Experience

```{r research-experience}
ezpickr::pick("../data/research-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Teaching Experience

```{r teaching-experience}
ezpickr::pick("../data/teaching-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Publications

## Refereed Journal Papers

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_journals}
:::
\endgroup

## Papers in Refereed Conference Proceedings

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_proceedings}
:::
\endgroup

## Publications in Healthcare

* I have contributed to the following publications for their methods and research designs.

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_healthcare}
:::
\endgroup

# Presentations

## Peer-Reviewed Conference Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../data/poster.txt")`

\endgroup

# Software Developments and Publications

## Data Science Packages in Comprehensive R Archive Network (CRAN)

<!-- ```{r R-package, echo = FALSE, cache = FALSE, eval = FALSE}
knitr::write_bib(c('ezpickr', 'mboxr', 'youtubecaption'), "../bib/R_packages.bib")
#R_package <- suppressMessages(RefManageR::ReadBib("../bib/R_packages.bib", check = FALSE))
#RefManageR:::print.BibEntry(R_package)
####vitae::bibliography_entries("../bib/R_packages.bib")
``` -->

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_R_packages}
:::
\endgroup

## Open-Source Project on GitHub

<!-- ```{r github, echo = FALSE, cache = FALSE, eval=T}
#knitr::write_bib(c('tactileR', 'ezviewr', 'jladown', 'edmdown'), "../bib/github.bib")
#github <- suppressMessages(RefManageR::ReadBib("../bib/github.bib", check = FALSE))
#RefManageR:::print.BibEntry(github)
####vitae::bibliography_entries("../bib/github.bib")
``` -->

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_github_projects}
:::
\endgroup

## Officially Code_Contributing R Packages

* My [18 GitHub pull requests](https://github.com/pulls?q=is%3Apr+author%3Ajooyoungseo+archived%3Afalse+is%3Aclosed) have been peer-reviewed and merged for active data science R packages:

```{r contribute}
#knitr::write_bib(c('bookdown', 'distill', 'BrailleR', 'wordcountaddin'), "../bib/contribute.bib")
ezpickr::pick("../data/contribute.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Awards and Honors

```{r award}
ezpickr::pick("../data/award.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Grants

```{r grant}
ezpickr::pick("../data/grant.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

## Invited Guest Lectures

```{r talk}
ezpickr::pick("../data/talk.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why, .protect = TRUE)
```
