---
graphics: yes
name: JooYoung
surname: Seo
headcolor: 414141
#qualifications: 
position: "Ph.D."
pronouns: he/him/his
address: "614 E. Daniel St. | Room 5158, Champaign, IL 61820"
phone: "+1 217-333-2671"
www: jooyoungseo.github.io
email: "jseo1005@illinois.edu"
twitter: seo_jooyoung
github: jooyoungseo
linkedin: jooyoungseo
aboutme: |
  I am a learning scientist, data-science/software engineer, and internationally certified accessibility professional.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa6-cv.csl"
nocite: "@*"
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \fancyhead[R]{\thepage}
knit: (function(input, ...) {bookdown::render_book(input, output_format = "all", ...)})
bibliography_selected: "bib/selected.bib"
bibliography_journals: "bib/journal.bib"
bibliography_proceedings: "bib/proceedings.bib"
bibliography_healthcare: "bib/healthcare.bib"
bibliography_working_paper: "bib/working_paper.bib"
bibliography_R_packages: "bib/R_packages.bib"
bibliography_github_projects: "bib/github.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(vroom)
```

<!--chapter:end:index.Rmd-->

# Education

```{r education}
vroom::vroom("data/education.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:education.Rmd-->

# Professional Appointment

```{r appointment}
vroom::vroom("data/appointment.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:appointment.Rmd-->


# Certificates

```{r certificate}
vroom::vroom("data/certificate.csv") %>%
  filter(with != "IBM") %>%
  vitae::detailed_entries(what, when, with, .protect = FALSE)
```

<!--chapter:end:certificate.Rmd-->

# Publications

* The following notations only apply to September 2021 and after.

`#`: derived from the candidate’s thesis.

`*`: publication that has undergone stringent editorial review by peers.

`+`: publication that was invited and carries special prestige and recognition.

<!-- # Selected Publications -->
<!--  -->
<!-- ::: {#refs_selected} -->
<!-- ::: -->

## Refereed Journal Papers

::: {#refs_journals}
:::

## Papers in Refereed Conference Proceedings

::: {#refs_proceedings}
:::

<!--chapter:end:publication.Rmd-->

## Publications in Healthcare

::: {#refs_healthcare}
:::


## Working Papers under Revision or Review

::: {#refs_working_paper}
:::

<!--chapter:end:healthcare.Rmd-->

# Conference Presentations and Invited Talks

`r knitr::knit_child("data/poster_short.txt")`

<!-- ## Invited Guest Lectures -->
<!-- ```{r talk}
vroom::vroom("data/talk.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why, .protect = TRUE)
``` -->

<!--chapter:end:presentation.Rmd-->

# Software Developments and Publications

## Data Science Packages in Comprehensive R Archive Network (CRAN)

<!-- ```{r R-package, echo = FALSE, cache = FALSE, eval = FALSE}
knitr::write_bib(c("ezpickr", "mboxr", "youtubecaption"), "bib/R_packages.bib")
# R_package <- suppressMessages(RefManageR::ReadBib("bib/R_packages.bib", check = FALSE))
# RefManageR:::print.BibEntry(R_package)
#### vitae::bibliography_entries("bib/R_packages.bib")
``` -->

::: {#refs_R_packages}
:::

\newpage

## Open-Source Project on GitHub

<!-- ```{r github, echo = FALSE, cache = FALSE, eval=T}
# knitr::write_bib(c('tactileR', 'ezviewr', 'jladown', 'edmdown'), "bib/github.bib")
# github <- suppressMessages(RefManageR::ReadBib("bib/github.bib", check = FALSE))
# RefManageR:::print.BibEntry(github)
#### vitae::bibliography_entries("bib/github.bib")
``` -->

::: {#refs_github_projects}
:::

## Officially Code_Contributing R Packages

* [My GitHub pull requests](https://github.com/pulls?q=is%3Apr+author%3Ajooyoungseo+archived%3Afalse+is%3Aclosed) have been peer-reviewed and merged for active data science R packages:

```{r contribute}
# knitr::write_bib(c('bookdown', 'distill', 'BrailleR', 'wordcountaddin'), "bib/contribute.bib")
vroom::vroom("data/contribute.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:software_dev.Rmd-->

# Teaching Experience
<!-- ```{r teaching-experience}
vroom::vroom("data/teaching-experience.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
``` -->

* IS 407: Introduction to Data Science (spring 2022).

* IS 569: Internship (spring 2022). *Advised Ankita Khiratkar (MS IM)*.

* IS 589: Independent Study (spring 2022). *Advised Chetna Beri (MS IM)*.

* INFO 399: Individual Study (spring 2022). *Advised Leo Zhang (CS undergrad --> Currently, Master's student at UCLA Data Science dept)*.

* IS 389: Independent Study (spring 2022). *Advised Miso Kim (BS IS)*.

* IS 226: Introduction to Human-Computer Interaction (fall 2021). *Co-teaching with Dr. Yang Wang*.

* Served as an annual review committee member for iSchool Ph.d. student Smirity Kaushik (advisor Dr. Yang Wang) (spring 2022).

* Served as a field exam committee member for iSchool Ph.D. candidate Jaihyun Park (advisor Dr. Ryan Cordell) (spring 2022).

<!--chapter:end:teaching_exp.Rmd-->


# Grants

<!-- ```{r grant, eval = FALSE}
vroom::vroom("data/grant.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
``` -->

Seo, J. (PI) (submitted for May 2022 - May 2023). Improving Accessible Reproducibility for Data Science Publishing System. *RStudio PBC*. Requested funding amount: \$54,327.

Ludäscher, B. (PI), Seo, J. (Co-PI), & Vilhuber, L. (Co-PI) (submitted for Aug 2022 - Aug 2023). Whole Tale Accessibility Project. *The Sloan Foundation*. Requested funding amount: \$225,000.

Choi, S. (PI), Seo, J. (Co-PI), Mahoney, M. (Co-PI), Davies, C. (Co-PI) (submitted for July 2022 - December 2023). Understanding the Sleep Patterns of Blind Populations Using Self-Tracking Technologies - What is It Like and How can We Support It?. *The Center on Health, Aging, and Disability, College of Applied Health Sciences*. Requested funding amount: \$30,000.

Seo, J. (PI), & Koh, K. (Co-PI) (submitted for Aug 2022 - May 2025). Promoting Computational Thinking Skills for Blind and Visually Impaired Teens through Accessible Library Makerspaces. *IMLS (Institute of Museum and Library Services) National Leadership Grants for Libraries*. Requested funding amount: \$498,638.

Seo, J. (PI) (awarded: unrestricted beyond Jan 2022 - December 2022). Data Accessibilization: Making Data Science Education Accessible for Blind Learners. *Wallace Foundation grant, Emerging Scholars Program of the International Society of the Learning Sciences (ISLS)*. Awarded funding amount: \$10,000.

<!--chapter:end:grant.Rmd-->

# Awards and Honors

```{r award}
vroom::vroom("data/award.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:award.Rmd-->

# Service

```{r service}
vroom::vroom("data/service.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:service.Rmd-->

# Current Memberships

  * International Society of the Learning Sciences (ISLS)
  * Association for Computing Machinery (ACM)
  * American Statistical Association (ASA)
  * International Society for Quantitative Ethnography (ISQE)
  * International Association of Accessibility Professionals (IAAP)
  * International Educational Data Mining Society (IEDMS)
  

<!--chapter:end:membership.Rmd-->

