%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{JooYoung}{Seo}

\position{Ph.D.}
\address{614 E. Daniel St.~\textbar{} Room 5158, Champaign, IL 61820}

\pronouns{he/him/his}
\mobile{+1 217-333-2671}
\email{\href{mailto:jseo1005@illinois.edu}{\nolinkurl{jseo1005@illinois.edu}}}
\homepage{jooyoungseo.github.io}
\github{jooyoungseo}
\linkedin{jooyoungseo}
\twitter{seo\_jooyoung}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{I am a learning scientist, data-science/software developer, and
internationally certified accessibility professional.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{xurl}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {November 02, 2023}
    {JooYoung Seo~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Ph.D. in Learning, Design, and Technology}{The Pennsylvania State University}{University Park, PA}{2021}{\begin{cvitems}
\item Dissertation Title: ``Discovering Informal Learning Cultures of Blind Individuals Pursuing STEM Disciplines: A Computational Ethnography Using Public Listserv Archives.''
\item Committee members: Drs. Gabriela T. Richard (adviser; dissertation chair), Roy B. Clariana, ChanMin Kim, and Mary Beth Rosson.
\end{cvitems}}
    \cventry{M.Ed. in Learning, Design, and Technology}{The Pennsylvania State University}{University Park, PA}{2016}{}\vspace{-4.0mm}
    \cventry{Double B.A. in Education, English Literature}{Sungkyunkwan University}{Seoul, South Korea}{2014}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{professional-appointment}{%
\section{Professional Appointment}\label{professional-appointment}}

\begin{cventries}
    \cventry{Assistant Professor}{School of Information Sciences}{University of Illinois at Urbana-Champaign}{Sep. 2021 - Present}{}\vspace{-4.0mm}
    \cventry{Faculty Affiliate}{National Center for Supercomputing Applications}{University of Illinois at Urbana-Champaign}{Dec. 2021 - Present}{}\vspace{-4.0mm}
    \cventry{Faculty Affiliate}{Illinois Informatics Institute}{University of Illinois at Urbana-Champaign}{Sep. 2021 - Present}{}\vspace{-4.0mm}
    \cventry{Faculty Affiliate}{IDEA (Inclusion, Diversity, Equity, and Access) Institute}{University of Illinois at Urbana-Champaign}{Jan. 2022 - Present}{}\vspace{-4.0mm}
    \cventry{Affiliate Scientist}{Rehabilitation Engineering Research Center (RERC) on Blindness and Low Vision}{Smith-Kettlewell Eye Research Institute}{Jul. 2023 - Present}{}\vspace{-4.0mm}
    \cventry{Software Engineer Intern}{RStudio}{Boston, MA}{May. 2020 - Aug. 2020}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{grants}{%
\section{Grants}\label{grants}}

\hypertarget{awarded-grants}{%
\subsection{Awarded Grants}\label{awarded-grants}}

\begin{itemize}
\item
  ``Beyond Visuals: Improving Accessibility of Data Curation and
  Multi-Modal Representations for People of all Abilities through
  Reproducible Workflows,'' PI, Institute of Museum and Library Services
  (IMLS) Laura Bush 21st Century Librarian Program, Grant
  \#RE-254891-OLS-23, \$649,921, Aug 2023 - July 2026 (ongoing).
\item
  ``Promoting Computational Thinking Skills for Blind and Visually
  Impaired Teens through Accessible Library Makerspaces,'' PI, Institute
  of Museum and Library Services (IMLS) National Leadership Grants,
  Grant \#LG-252360-OLS-22, \$498,638, Aug 2022 - May 2025 (ongoing).
\item
  ``Inclusive Data Science: Fostering Accessibility and Reproducibility
  with Multimodal Learning Strategies,'' PI, Teach Access Faculty
  Grants, Tier 3, \$5,000, May 2023 - May 2024 (ongoing).
\item
  ``Improving Accessible Reproducibility for Data Science Publishing
  System,'' PI, Posit PBC (unrestricted gift), \$54,327, May 2022 -
  Present (ongoing).
\item
  ``Co-designing an Alexa-Based Conversational mHealth System with
  Visually Impaired People to Promote Physical Activities,'' Co-PI,
  Center on Health, Aging, and Disability's (CHAD) Pilot Grant Program
  at the University of Illinois at Urbana-Champaign, \$29,866, 2023-2024
  (ongoing).
\item
  ``Category I: Crossing the Divide Between Today's Practice and
  Tomorrow's Science,'' Senior Personnel, National Science Foundation
  (NSF), Grant \#2005572, \$10,000,000.00, Oct 2021 - Sept 30, 2026 (.5
  FTE academic year) (ongoing).
\item
  ``Insight without Sight: Enhancing Data Literacy through Multimodal
  Data Science Education - Smith-Kettlewell Summer Institute,'' Subaward
  PI, Rehabilitation Engineering Research Centers (RERC) Program: RERC
  on Blindness and Low Vision, National Institute on Disability,
  Independent Living, and Rehabilitation Research (NIDILRR), Grant
  \#90REGE0018-01-00, \$11,975, July 17, 2023 - August 11, 2023
  (completed).
\item
  ``Data Accessibilization: Making Data Science Education Accessible for
  Blind Learners,'' PI, Wallace Foundation, Emerging Scholars Program,
  International Society of the Learning Sciences, \$10,000, Jan 2022 -
  Dec 2022 (completed).
\end{itemize}

\hypertarget{under-review-grants}{%
\subsection{Under-Review Grants}\label{under-review-grants}}

\begin{itemize}
\tightlist
\item
  ``Collaborative Research: SpatioTemporal Representations for
  Information and Data Equity: An Interactive AudioTactile System for
  BVI Data Scientists,'' PI (at UIUC), National Science Foundation
  (NSF), Workplace Equity for Persons with Disabilities in STEM and STEM
  Education (nsf23593), \$573,548 (for UIUC) out of \$1,499,917 total,
  July 2024 - June 2028 (under review).
\end{itemize}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begin{itemize}
\tightlist
\item
  The following notations only apply to September 2021 and after.
\end{itemize}

\texttt{\#}: derived from the candidate's thesis.

\texttt{*}: publication that has undergone stringent editorial review by
peers.

\texttt{+}: publication that was invited and carries special prestige
and recognition.

\hypertarget{refereed-journal-papers}{%
\subsection{Refereed Journal Papers}\label{refereed-journal-papers}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-leePersonalHealthData2023}{}%
1.\textsuperscript{\emph{\textbf{*}}} Lee, J. G. W., Lee, K., Lee, B.,
Choi, S., \textbf{Seo, J.}, \& Choe, E. K. (2023). Personal Health Data
Tracking by Blind and Low-Vision People: Survey Study. \emph{Journal of
Medical Internet Research}, \emph{25}(1), e43917.
\url{https://doi.org/10.2196/43917}

\leavevmode\hypertarget{ref-moonRevisitingMultimediaLearning2023}{}%
2.\textsuperscript{\emph{\textbf{*}}} Moon, J., Choi, G. W., \&
\textbf{Seo, J.} Y. (2023). Revisiting multimedia learning design
principles in virtual reality-based learning environments for autistic
individuals. \emph{Virtual Reality}.
\url{https://doi.org/10.1007/s10055-023-00856-2}

\leavevmode\hypertarget{ref-moonLearningAnalyticsSeamless2023a}{}%
3.\textsuperscript{\emph{\textbf{*}}} Moon, J., Lee, D., Choi, G. W.,
\textbf{Seo, J.}, Do, J., \& Lim, T. (2023). Learning analytics in
seamless learning environments: A systematic review. \emph{Interactive
Learning Environments}, \emph{0}(0), 1--18.
\url{https://doi.org/10.1080/10494820.2023.2170422}

\leavevmode\hypertarget{ref-seoTeachingVisualAccessibility2023}{}%
4.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, \& Dogucu, M.
(2023). Teaching Visual Accessibility in Introductory Data Science
Classes with Multi-Modal Data Representations. \emph{Journal of Data
Science}, 1--14. \url{https://doi.org/10.6339/23-JDS1095}

\leavevmode\hypertarget{ref-seo2022csun}{}%
5.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, \& Choi, S.
(2022). Are blind people considered a part of scientific knowledge
producers?: Accessibility report on top-10 scie journal systems using a
tripartite evaluation approach. \emph{Journal on Technology and Persons
with Disabilities}.

\leavevmode\hypertarget{ref-seoScopingReviewThree2022}{}%
6.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, Moon, J., Choi,
G. W., \& Do, J. (2022). A Scoping Review of Three Computational
Approaches to Ethnographic Research in Digital Learning Environments.
\emph{TechTrends}, \emph{66}(1), 102--111.
\url{https://doi.org/10.1007/s11528-021-00689-3}

\leavevmode\hypertarget{ref-doi:10.1080ux2f09286586.2020.1863993}{}%
7. Choi, S., \& \textbf{Seo, J.} (2021). Trends in healthcare research
on visual impairment and blindness: Use of bibliometrics and
hierarchical cluster analysis. \emph{Ophthalmic Epidemiology},
\emph{28}(4), 277--284.
\url{https://doi.org/10.1080/09286586.2020.1863993}

\leavevmode\hypertarget{ref-seoSCAFFOLDingAllAbilities2021a}{}%
8.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, \& Richard, G.
T. (2021). SCAFFOLDing All Abilities into Makerspaces: A Design
Framework for Universal, Accessible and Intersectionally Inclusive
Making and Learning. \emph{Information and Learning Sciences},
\emph{122}(11/12), 795--815.
\url{https://doi.org/10.1108/ILS-10-2020-0230}

\leavevmode\hypertarget{ref-seo2019maker}{}%
9. \textbf{Seo, J.} (2019). Is the maker movement inclusive of ANYONE?:
Three accessibility considerations to invite blind makers to the making
world. \emph{TechTrends}, \emph{63}(5), 514--520.
\url{https://doi.org/10.1007/s11528-019-00377-3}

\leavevmode\hypertarget{ref-seo2019arow}{}%
10. \textbf{Seo, J.}, \& McCurry, S. (2019). LaTeX is not easy: Creating
accessible scientific documents with r markdown. \emph{Journal on
Technology and Persons with Disabilities}, \emph{7}, 157--171.

\hypertarget{papers-in-refereed-conference-proceedings}{%
\subsection{Papers in Refereed Conference
Proceedings}\label{papers-in-refereed-conference-proceedings}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-289508}{}%
1.\textsuperscript{\emph{\textbf{*}}} Kaushik, S., Barbosa, N. M., Yu,
Y., Sharma, T., Kilhoffer, Z., \textbf{Seo, J.}, Das, S., \& Wang, Y.
(2023). GuardLens: Supporting safer online browsing for people with
visual impairments. \emph{Nineteenth Symposium on Usable Privacy and
Security (Soups 2023)}, 361--380.
\url{https://www.usenix.org/conference/soups2023/presentation/kaushik}

\leavevmode\hypertarget{ref-kimTrendCollaborationSTEM2023a}{}%
2.\textsuperscript{\emph{\textbf{*}}} Kim, S. H., Yoon, A., \&
\textbf{Seo, J.} (2023). Trend of Collaboration in STEM Education in
Informal Learning Institutions Based on IMLS-funded Projects.
\emph{Proceedings of the Association for Information Science and
Technology}, \emph{60}(1), 625--629.
\url{https://doi.org/10.1002/pra2.828}

\leavevmode\hypertarget{ref-parkExploringOnlineCommunity2023}{}%
3.\textsuperscript{\emph{\textbf{*}}} Park, J., \textbf{Seo, J.}, \&
Lee, J. Y. (2023). Exploring an Online Community of Blind Programmers by
Using Topic Modeling and Network Analysis. \emph{Proceedings of the
Association for Information Science and Technology}, \emph{60}(1),
1096--1098. \url{https://doi.org/10.1002/pra2.956}

\leavevmode\hypertarget{ref-seoCodingNonVisuallyVisual2023}{}%
4.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, \& Rogge, M.
(2023). Coding Non-Visually in Visual Studio Code: Collaboration Towards
Accessible Development Environment for Blind Programmers.
\emph{Proceedings of the 25th International ACM SIGACCESS Conference on
Computers and Accessibility}, 1--9.
\url{https://doi.org/10.1145/3597638.3614550}

\leavevmode\hypertarget{ref-seoMAIDRMultimodalAccess2023}{}%
5.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, Xia, Y., Yam, Y.
J., \& McCurry, S. (2023). MAIDR: Multimodal Access and Interactive Data
Representation System for Inclusive Data Science Education.
\emph{Proceedings of the 3rd Annual Meeting of the International Society
of the Learning Sciences}, 51--54.

\leavevmode\hypertarget{ref-289496}{}%
6.\textsuperscript{\emph{\textbf{*}}} Zhang, Z. (., Kaushik, S.,
\textbf{Seo, J.}, Yuan, H., Das, S., Findlater, L., Gurari, D., Stangl,
A., \& Wang, Y. (2023). ImageAlly: A Human-AI hybrid approach to support
blind people in detecting and redacting private image content.
\emph{Nineteenth Symposium on Usable Privacy and Security (Soups 2023)},
417--436.
\url{https://www.usenix.org/conference/soups2023/presentation/zhang}

\leavevmode\hypertarget{ref-huh2022duoethnographic}{}%
7.\textsuperscript{\emph{\textbf{*}}} Huh, M., \& \textbf{Seo, J.}
(2022). A duoethnographic study of a mixed-ability team in a
collaborative group programming project. In A. Weinberger, W. Chen, D.
Hernández-Leo, \& B. Chen (Eds.), \emph{Proceedings of the 15th
international conference on computer-supported collaborative learning -
cscl 2022} (pp. 471--474). International Society of the Learning
Sciences.

\leavevmode\hypertarget{ref-leeCollabAllyAccessibleCollaboration2022a}{}%
8.\textsuperscript{\emph{\textbf{*}}} Lee, C. Y. P., Zhang, Z.,
Herskovitz, J., \textbf{Seo, J.}, \& Guo, A. (2022). CollabAlly:
Accessible Collaboration Awareness in Document Editing. \emph{CHI
Conference on Human Factors in Computing Systems}, 1--17.
\url{https://doi.org/10.1145/3491102.3517635}. \emph{Honorable mention
award}.

\leavevmode\hypertarget{ref-teachingvisualaccessibility2022}{}%
9.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, \& Dogucu, M.
(2022). Teaching visual accessibility in the introductory data science
classes: Why, what, when, and how. \emph{The 2022 Symposium on Data
Science \& Statistics}.

\leavevmode\hypertarget{ref-lee2021collabally}{}%
10.\textsuperscript{\emph{\textbf{*}}} Lee, C. Y. P., Zhang, Z.,
Herskovitz, J., \textbf{Seo, J.}, \& Guo, A. (2021). CollabAlly:
Accessible collaboration awareness in document editing. \emph{The 23rd
International Acm Sigaccess Conference on Computers and Accessibility},
1--4. \url{https://doi.org/10.1145/3441852.3476562}

\leavevmode\hypertarget{ref-seo2020coding}{}%
11. \textbf{Seo, J.}, \& Richard, G. T. (2020). Coding through touch:
Exploring and re-designing tactile making activities with learners with
visual dis/abilities. In M. Gresalfi \& I. Horn (Eds.),
\emph{Interdisciplinarity in the learning sciences, 14th international
conference of the learning sciences (icls) 2020} (Vol. 3, pp.
1373--1380). International Society of the Learning Sciences (ISLS).

\leavevmode\hypertarget{ref-seo2019discovering}{}%
12. \textbf{Seo, J.} (2019). Discovering informal learning cultures of
blind individuals pursuing stem disciplines: A quantitative ethnography
using listserv archives. \emph{The First International Conference on
Quantitative Ethnography: Doctoral Consortium}, S66--S67. \emph{Awarded
the best Doctoral Consortium Proposal Cengage fellowship}.

\leavevmode\hypertarget{ref-seo2018making}{}%
13. \textbf{Seo, J.} (2018). Accessibility and inclusivity in making:
Engaging learners with all abilities in making activities. In
\emph{Proceedings of the 3rd learning sciences graduate student
conference} (pp. 141--142). LSGSC Planning Team.

\leavevmode\hypertarget{ref-seo2018accessibility}{}%
14. \textbf{Seo, J.}, \& Richard, G. T. (2018). Accessibility, making
and tactile robotics: Facilitating collaborative learning and
computational thinking for learners with visual impairments. In J. Kay
\& R. Luckin (Eds.), \emph{Rethinking learning in the digital age:
Making the learning sciences count, 13th international conference of the
learning sciences (icls) 2018} (Vol. 3, pp. 1755--1757). International
Society of the Learning Sciences (ISLS).

\leavevmode\hypertarget{ref-konecki2017role}{}%
15. Konecki, M., Lovrenčić, S., \textbf{Seo, J.}, \& LaPierre, C.
(2017). The role of ict in aiding visually impaired students and
professionals. \emph{Proceedings of the 11th Multidisciplinary Academic
Conference}, 148.

\leavevmode\hypertarget{ref-seo2017embracing}{}%
16. \textbf{Seo, J.}, AlQahtani, M., Ouyang, X., \& Borge, M. (2017).
Embracing learners with visual impairments in cscl. In B. K. Smith, M.
Borge, E. Mercier, \& K. Y. Lim (Eds.), \emph{Making a difference:
Prioritizing equity and access in cscl, 12th international conference on
computer supported collaborative learning (cscl) 2017} (Vol. 2, pp.
573--576). International Society of the Learning Sciences (ISLS).

\hypertarget{book-chapters}{%
\subsection{Book Chapters}\label{book-chapters}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-SeoDogucu2023}{}%
1.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, \& Dogucu, M.
(2024). Data science and accessibility. In A. Ko, R. Ladner, \& A. Oleso
(Eds.), \emph{Teaching accessible computing}. University of Washington.

\hypertarget{publications-in-healthcare}{%
\subsection{Publications in
Healthcare}\label{publications-in-healthcare}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-doi:10.1080ux2f01612840.2019.1705944}{}%
1. Choi, S., \& \textbf{Seo, J.} (2020). An exploratory study of the
research on caregiver depression: Using bibliometrics and lda topic
modeling. \emph{Issues in Mental Health Nursing}, 1--10.
\url{https://doi.org/10.1080/01612840.2019.1705944}

\leavevmode\hypertarget{ref-doi:10.1111ux2fnuf.12328}{}%
2. Choi, S., \& \textbf{Seo, J.} (2019). Analysis of caregiver burden in
palliative care: An integrated review. \emph{Nursing Forum},
\emph{54}(2), 280--290. \url{https://doi.org/10.1111/nuf.12328}

\leavevmode\hypertarget{ref-choi2019heart}{}%
3. Choi, S., \& \textbf{Seo, J.} (2019). Heart failure research using
text mining: A systematic review. \emph{NURSING RESEARCH}, \emph{68}(2),
E119--E120.

\leavevmode\hypertarget{ref-choi2019trends}{}%
4. Choi, S., \& \textbf{Seo, J.} (2019). Trends in self-management among
adults with heart failure from 2011 to 2016 using the national health
and nutrition examination surveys. \emph{Journal of Cardiac Failure},
\emph{25}(8), S4. \url{https://doi.org/10.1016/j.cardfail.2019.07.540}

\leavevmode\hypertarget{ref-choi2019exploring}{}%
5. Choi, S., \textbf{Seo, J.}, \& Kitko, L. (2019). Exploring the lived
experience of a family member with advanced heart failure: Using a text
mining approach. \emph{The First International Conference on
Quantitative Ethnography: Poster Session}, S8--S9.

\leavevmode\hypertarget{ref-choi2018effects}{}%
6. Choi, S., \& \textbf{Seo, J.} (2018). Effects of nonpharmacological
interventions for fatigue in patients with heart failure: A systematic
review and meta-analysis. \emph{Journal of Cardiac Failure},
\emph{24}(8), S73--S74.

\hypertarget{working-papers-under-revision-or-review}{%
\subsection{Working Papers under Revision or
Review}\label{working-papers-under-revision-or-review}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-lee2024identify}{}%
1.\textsuperscript{\emph{\textbf{*}}} Lee, J., Lee, B., Choi, S.,
\textbf{Seo, J.}, \& Choe, E. K. (under review-). Identify, adapt,
persist: The journey of blind and low-vision individuals with personal
health technologies. \emph{Proceedings of the 2024 Chi Conference on
Human Factors in Computing Systems}.

\leavevmode\hypertarget{ref-moon2023navigating}{}%
2.\textsuperscript{\emph{\textbf{*}}} Moon, J., \textbf{Seo, J.}, \&
Awoyemi, D. (under review-). Navigating social complexity: The
synergistic use of chatgpt and epistemic network analysis for social
skills assessment in autistic children in virtual reality-based
training. \emph{Journal of Computer Assisted Learning}.

\leavevmode\hypertarget{ref-seo2024maidr}{}%
3.\textsuperscript{\emph{\textbf{*}}} \textbf{Seo, J.}, Xia, Y., Lee,
B., McCurry, S., \& Yam, Y. J. (under review-). MAIDR: Making
statistical visualizations accessible with multimodal data
representation. \emph{Proceedings of the 2024 Chi Conference on Human
Factors in Computing Systems}.

\hypertarget{conference-presentations-and-invited-talks}{%
\section{Conference Presentations and Invited
Talks}\label{conference-presentations-and-invited-talks}}

\textbf{Seo, J.} (2023, November). \emph{Insight Over Eyesight: My
Journey as a Blind Data Scientist}. Invited talk at the Chicago
Lighthouse Career Fair, Chicago, IL (virtual).

\textbf{Seo, J.} (2023, November). \emph{Beyond Sight: Envisioning Data
Science Through Multimodal Access}. Invited as a keynote speaker at the
2023 UIUC iSchool's Research Showcase, Champaign, IL.

\textbf{Seo, J.} (2023, November). \emph{Multimodal Data Representation
for Inclusive Data Science Education}. Invited talk at the UIUC CI590
DELTA Seminar, Champaign, IL.

\textbf{Seo, J.} (2023, July). \emph{Screen Reader User Experience Deep
Dive}. Invited talk at the Microsoft Visual Studio Code Team, virtual.

\textbf{Seo, J.} (2023, June). \emph{Perceiving Beyond Vision: My
Journey Through Dreamscapes, Numerical Cognition, and a Blind Critique
of Inclusive Data Visualization}. Invited talk at the Dagstuhl Inclusive
Data Visualization Workshop, Dagstuhl, Germany.

\textbf{Seo, J.} (2023, May). \emph{Enhancing Accessibility in
Programming and Fostering Inclusive Data Science via Multimodal
Strategies}. Invited talk at the Campus Research Computing Consortium,
virtual.

Invited panel (2023, May): \emph{Human Computer Relationships
{\textbf{???}}: Embodiment, Inclusive Design, Accessibility, and
Emerging Technologies for Learning}, hosted by PhET Interactive
Simulations at University of Colorado Boulder.

Invited demo by Microsoft (2023, April): \emph{VSCode Accessibility}. VS
Code Day 2023: \url{https://m.youtube.com/watch?v=X3qUfOB3x8Q}

Invited panel (2022, December): \emph{Integrating Accessibility into a
Computing Career}, hosted by Associate Professor Stacy Branham at
Informatics of the University of California, Irvine. (virtual).

\textbf{Seo, J.} (2022, November). \emph{Accessible Library
Makerspaces}. Invited talk at the UIUC iSchool IS571: Accessibility in
Library Resources, Champaign, IL (virtual).

\textbf{Seo, J.} (2022, September). \emph{Digital Accessibility}.
Invited panel at the INFOcon 2022, virtual.

\textbf{Seo, J.} (2022, April). \emph{Accessible Data Visualization in a
Reproducible Way}. Invited talk at Champaign-Urbana Data Science User
Group, Champaign, IL (virtual).

\textbf{Seo, J.} (2022, March). \emph{Understanding Multi-Modality of
Blind People Towards Inclusive STEM Learning}. Invited talk at the UIUC
iSchool Proseminar, Champaign, IL (virtual).

\textbf{Seo, J.} (2022, March). \emph{Universal Design = Usability
\texttt{*} Accessibility (With Practical Examples Beyond Conceptual
Frameworks)}. Invited talk at INTE 535 Analysis, Implementation, and
Evaluation of Assistive Technology. Instructional Technology program of
the University of Alabama, Tuscaloosa, AL (virtual).

\textbf{Seo, J.} (2022, March). \emph{Your Condition is Not Your
Conclusion}. Invited talk at HTM4311: Hotel Professional Development at
the Hong Kong Polytechnic University (virtual).

\textbf{Seo, J.} (2021, November). \emph{SCAFFOLDing All Abilities into
Makerspaces}. Invited talk at the UIUC iSchool IS582: Make, Design, \&
Learn in Libraries, Champaign, IL (virtual).

\textbf{Seo, J.} (2021, October). \emph{Non-Visual Strategies for Making
Statistical-Computing Accessible}. Lightening talk at the National
Center for Supercomputing Applications, Champaign, IL.

\textbf{Seo, J.} (2021, September). \emph{Accessibility of Science
Beyond Content Accessibility}. Talk presented at the Argonne National
Laboratory (Maths and Computer Science Division):
\emph{\url{https://www.anl.gov/event/accessibility-of-science-beyond-content-accessibility}}.

Invited panel (2021, August). DO-IT Neuroscience for Neurodiverse
Learners Faculty panel at the University of Washington, virtual.

\textbf{Seo, J.} (2021, June). \emph{How to Learn to Code}. Invited Talk
presented at the Nature, Webcast:
\emph{\url{https://doi.org/10.1038/d41586-021-01638-z}}.

\textbf{Seo, J.}, \& Richard, G. T. (2021, February). \emph{Uncovering
latent topics of blind people in computer science: structural topic
modeling for an email corpus}. Poster presented at the 2nd International
Conference on Quantitative Ethnography (ICQE), Malibu, CA.

Donegan, S. R., Porter, C., Fogel, A., \textbf{Seo, J.}, Choi, S., \&
Eagan, B. (2021, February). \emph{U.S. media coverage during COVID-19:
an epistemic network analysis of bias, topic, and trajectory}. Poster
presented at the 2nd International Conference on Quantitative
Ethnography (ICQE), Malibu, CA.

\textbf{Seo, J.} (2021, January). \emph{Accessible data science beyond
visual models}. Talk presented at the rstudio::global(2021), Virtual:
\emph{\url{https://global.rstudio.com/student/page/40617}}.

\textbf{Seo, J.} (2020, September). \emph{Discovering knowledge sharing
patterns of blind people pursuing STEM disciplines: data science and
computational linguistics on large-scale email corpora}. Poster
presented at the Doctoral Consortium of the annual meeting of the ACM
Richard Tapia Celebration of Diversity in Computing, virtual.
\emph{Awarded the Qualcomm scholarship}.

\textbf{Seo, J.}, \& Richard, G. T. (2020, April). \emph{Maker
inclusivity = maker accessibility: further interrogations for diverse
participation}. Poster presented at the annual meeting of the American
Educational Research Association (AERA), Virtual.

\textbf{Seo, J.}, \& Richard, G. T. (2018, April). \emph{Furthering
inclusivity in making: a framework for accessible design of makerspaces
for learners with disabilities}. Poster presented at the annual meeting
of the American Educational Research Association (AERA), New York City,
NY.

Bunag, T., Aniela, L., Nielsen, M. C., \& \textbf{Seo, J.} (2017,
November). \emph{The rapidly changing world of accessible online
learning}. Presented at the Panel Discussion: DDL - Accessible Online
Learning In Concurrent Presentation of the Association for Educational
Communications and Technology (AECT), Jacsonville, FL.

\textbf{Seo, J.} (2017, September). \emph{Tactile access to visualized
statistical data using R}. Poster presented at the annual meeting of the
ACM Richard Tapia Celebration of Diversity in Computing, Atlanta, GA.

Liao, J., Patcyk, M., \textbf{Seo, J.}, \& Hooper, S. (2016, October).
\emph{Using hierarchical linear modeling to measure growth rate in a
gamified CBM environment}. Paper presented at the annual meeting of the
Northeastern Educational Research Association (NERA), Trumbull, CT.

\textbf{Seo, J.} (2016, March). \emph{Engaging blind learners in
statistics study using R}. Presented at the annual meeting of the
Teaching and Learning with Technology (TLT) Symposium, University Park,
PA.

Kim, K., \textbf{Seo, J.}, \& Clariana, R. B. (2016, March).
\emph{Automatic knowledge structure measure in online courses}.
Presented at the annual meeting of the Teaching and Learning with
Technology (TLT) Symposium, University Park, PA.

\textbf{Seo, J.} (2015, November). \emph{Assistive technologies for
equal access in general education}. Presented at the annual meeting of
the Association for Educational Communications and Technology (AECT),
Indianapolis, IN.

\textbf{Seo, J.}, \& Park, E. (2015, October). \emph{The more
accessible, the more potential: simple tips for online accessibility}.
Presented at the Technology and Learning Conference, Blue Bell, PA.

\hypertarget{media-coverage}{%
\section{Media Coverage}\label{media-coverage}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-heckelInformationSciencesProfessora}{}%
1. Heckel, J. (2023, September 29). \emph{Information sciences professor
developing tool to make data visualizations accessible to blind
researchers, students}. News Bureau University of Illinois
Urbana-Champaign. \url{https://news.illinois.edu/view/6367/107909242}

\leavevmode\hypertarget{ref-mccallen2023data}{}%
2. McCallen, B. (2023, November 3). \emph{Data visualization for the
blind}.
\url{https://speakingoutfortheblind.weebly.com/list-of-episodes-and-show-news/for-more-information-episode-329-data-visualization-tool-for-the-blind}

\leavevmode\hypertarget{ref-katsnelsonTheseToolsHelp2023}{}%
3. Katsnelson, A. (2023). These tools help visually impaired scientists
read data and journals. \emph{Nature}, \emph{615}(7951, 7951), 362--363.
\url{https://doi.org/10.1038/d41586-023-00645-6}

\hypertarget{software-developments-and-publications}{%
\section{Software Developments and
Publications}\label{software-developments-and-publications}}

\hypertarget{data-science-packages-in-comprehensive-r-archive-network-cran}{%
\subsection{Data Science Packages in Comprehensive R Archive Network
(CRAN)}\label{data-science-packages-in-comprehensive-r-archive-network-cran}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-Iannone_gt_Easily_Create}{}%
1. Iannone, R., Cheng, J., Schloerke, B., Hughes, E., Lauer, A., \&
\textbf{Seo, J.} (2023). \emph{gt: Easily Create Presentation-Ready
Display Tables} (Version 0.9.0).
\url{https://CRAN.R-project.org/package=gt}. \emph{Over 1.5M download}.

\leavevmode\hypertarget{ref-R-youtubecaption}{}%
2. \textbf{Seo, J.}, \& Choi, S. (2020). \emph{Youtubecaption:
Downloading youtube subtitle transcription in a tidy tibble data frame}.
\url{https://CRAN.R-project.org/package=youtubecaption}. \emph{Over 18K
download}.

\leavevmode\hypertarget{ref-R-ezpickr}{}%
3. \textbf{Seo, J.}, \& Choi, S. (2019). \emph{Ezpickr: Easy data import
using gui file picker and seamless communication between an excel and
r}. \url{https://CRAN.R-project.org/package=ezpickr}. \emph{Over 31K
download}.

\leavevmode\hypertarget{ref-R-mboxr}{}%
4. \textbf{Seo, J.}, \& Choi, S. (2019). \emph{Mboxr: Reading,
extracting, and converting an mbox file into a tibble}.
\url{https://CRAN.R-project.org/package=mboxr}. \emph{Over 25K
download}.

\newpage

\hypertarget{open-source-project-on-github}{%
\subsection{Open-Source Project on
GitHub}\label{open-source-project-on-github}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-R-edmdown}{}%
1. \textbf{Seo, J.} (2020). \emph{Edmdown: Writing a reproducible
article for journal of educational datamining in r markdown}.
\url{https://github.com/jooyoungseo/edmdown}. \emph{R package version
0.0.0.9000}.

\leavevmode\hypertarget{ref-R-islsdown}{}%
2. \textbf{Seo, J.}, Chan, T., Michaelis, J. E., \& Rosenberg, J. M.
(2020). \emph{Islsdown: Writing a reproducible conference paper for the
international society of the learning sciences annual meeting in r
markdown}. \url{https://github.com/jooyoungseo/islsdown}. \emph{R
package version 0.0.0.9000}.

\leavevmode\hypertarget{ref-R-jladown}{}%
3. \textbf{Seo, J.}, \& Rosenberg, J. M. (2020). \emph{Jladown: Writing
a reproducible article for journal of learning analytics in r markdown}.
\url{https://github.com/jooyoungseo/jladown}. \emph{R package version
0.0.0.9000}.

\leavevmode\hypertarget{ref-R-ezviewr}{}%
4. \textbf{Seo, J.} (2019). \emph{Ezviewr: View tidy data in preferable
spreadsheet}. \url{https://github.com/jooyoungseo/ezviewr}. \emph{R
package version 0.1.0}.

\leavevmode\hypertarget{ref-R-tactileR}{}%
5. \textbf{Seo, J.} (2019). \emph{TactileR: Converting r graphics into a
braille ready-to-print pdf}.
\url{https://github.com/jooyoungseo/tactileR}. \emph{R package version
0.1.0}.

\leavevmode\hypertarget{ref-webrender}{}%
6. \textbf{Seo, J.}, \& McCurry, S. (2019). \emph{AROW: Accessible
rmarkdown online writer}. \url{http://www.arowtool.com}

\hypertarget{officially-code_contributing-r-packages}{%
\subsection{Officially Code\_Contributing R
Packages}\label{officially-code_contributing-r-packages}}

\begin{itemize}
\tightlist
\item
  \href{https://github.com/pulls?q=is\%3Apr+author\%3Ajooyoungseo+archived\%3Afalse+is\%3Aclosed}{My
  GitHub pull requests} have been peer-reviewed and merged for active
  data science R packages:
\end{itemize}

\begin{cventries}
    \cventry{shiny: Web Application Framework for R}{Chang, W., Cheng, J., Allaire, J., Xie, Y., \& McPherson, J.}{https://cran.r-project.org/web/packages/shiny/}{2020}{\begin{cvitems}
\item Contributed to improving keyboard and TTS accessibility for input widgets.
\end{cvitems}}
    \cventry{vitae: Curriculum Vitae for R Markdown}{O'Hara-Wild, M., \& Hyndman, R.}{https://cran.r-project.org/web/packages/vitae/}{2020}{\begin{cvitems}
\item Contributed to enabling LaTeX engine customization.
\item Contributed to displaying multiple bibliographies based on lua filter.
\end{cvitems}}
    \cventry{rmarkdown: Dynamic Documents for R}{Allaire, J., Xie, Y., et al.}{https://cran.r-project.org/web/packages/rmarkdown/}{2019}{\begin{cvitems}
\item Contributed to improving ioslides\_presentation accessibility for screen reading software.
\end{cvitems}}
    \cventry{bookdown: Authoring Books and Technical Documents with R Markdown}{Xie, Y.}{https://cran.r-project.org/web/packages/bookdown/}{2019}{\begin{cvitems}
\item Developed context\_document2, github\_document2, beamer\_presentation2, html\_fragment2, html\_notebook2, html\_vignette2, ioslides\_presentation2, slidy\_presentation2 and rtf\_document2 functions to enable R markdown users to utilize cross-references for figures and tables through bookdown package.
\end{cvitems}}
    \cventry{distill: 'R Markdown' Format for Scientific and Technical Writing}{Allaire, J., Iannone, R., \& Xie, Y.}{https://cran.r-project.org/web/packages/distill/}{2019}{\begin{cvitems}
\item Contributed to displaying more metadata for journal article bib\_entries.
\item Improved screen reader accessibility for navigation bar.
\item Added missing Google Scholar meta tags for conference, technical report, and dissertation types.
\end{cvitems}}
    \cventry{wordcountaddin: Word counts and readability statistics in R markdown documents}{Marwick, B.}{https://git.io/JkJca}{2019}{\begin{cvitems}
\item Contributed to text\_stats() function for R markdown users to Get a word count and some other stats for selected text (excluding code chunks and inline code).
\end{cvitems}}
    \cventry{BrailleR: Improved Access for Blind Users}{Godfrey, A. J. R., Warren, D., Murrell, P., Bilton, T., \& Sorge, V.}{https://cran.r-project.org/web/packages/BrailleR/}{2019}{\begin{cvitems}
\item Contributed to BRLThis() function to enable blind R users to convert a graph into a pdf ready for embossing in Braille.
\end{cvitems}}
\end{cventries}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\begin{itemize}
\item
  IS 407: Introduction to Data Science (spring 2022-present).
\item
  IS 569: Internship (spring 2022). \emph{Advised Ankita Khiratkar (MS
  IM)}.
\item
  IS 589: Independent Study (spring 2022). \emph{Advised Chetna Beri (MS
  IM)}.
\item
  INFO 399: Individual Study (spring 2022). \emph{Advised Leo Zhang (CS
  undergrad --\textgreater{} Currently, Master's student at UCLA Data
  Science dept)}.
\item
  IS 389: Independent Study (spring 2022). \emph{Advised Miso Kim (BS
  IS)}.
\item
  IS 226: Introduction to Human-Computer Interaction (fall 2021).
  \emph{Co-teaching with Dr.~Yang Wang}.
\item
  Served as an annual review committee member for iSchool Ph.d. student
  Smirity Kaushik (advisor Dr.~Yang Wang) (spring 2022).
\item
  Served as a field exam committee member for iSchool Ph.D.~candidate
  Jaihyun Park (advisor Dr.~Ryan Cordell) (spring 2022).
\end{itemize}

\hypertarget{awards-and-honors}{%
\section{Awards and Honors}\label{awards-and-honors}}

\begin{cventries}
    \cventry{Qualcomm Scholarship}{ACM Richard Tapia Celebration of Diversity in Computing Conference}{Virtual}{Sep. 2020}{\begin{cvitems}
\item Selected as one of the outstanding doctoral consortium proposals.
\end{cvitems}}
    \cventry{2020 NextGen Leaders}{Disability:IN}{Alexandria, VA}{Feb. 2020 - Jul. 2020}{\begin{cvitems}
\item Selected as one of the leaders in the U.S. for diversity.
\end{cvitems}}
    \cventry{AccessSTEM Resume contest winners Award}{AccessComputing, University of Washington}{Seattle, WA}{Dec. 2019}{\begin{cvitems}
\item Sponsored by The National Science Foundation (NSF).
\end{cvitems}}
    \cventry{Best Doctoral Proposal Fellowship}{The First International Conference on Quantitative Ethnography}{Madison, WI}{Oct. 2019}{\begin{cvitems}
\item Sponsored by Cengage.
\end{cvitems}}
    \cventry{Andrew V. Kozak Memorial Fellowship}{The PDK Educational Foundation}{University Park, PA}{2019}{\begin{cvitems}
\item Awarded \$1,500 for research contribution to public education.
\end{cvitems}}
    \cventry{AERA Pre-Conference Travel Award}{The Spencer Foundation}{Toronto, ON, Canada}{Apr. 2019}{}\vspace{-4.0mm}
    \cventry{Delta Gamma Golden Anchor Award}{The Pennsylvania State University}{University Park, PA}{2015, 2017}{}\vspace{-4.0mm}
    \cventry{ACM Richard Tapia Celebration of Diversity in Computing Conference Scholarship}{The National Science Foundation (NSF)}{Atlanta, GA}{Sep. 2017}{\begin{cvitems}
\item Included free conference registration, shared hotel accommodations and a \$500 travel stipend.
\end{cvitems}}
    \cventry{ACM Student Research Competition Travel Award}{Microsoft Research}{Atlanta, GA}{Sep. 2017}{\begin{cvitems}
\item \$500 travel stipend was awarded for ACM TAPIA 2017 Student Research Competition (SRC).
\end{cvitems}}
    \cventry{CSUN Conference Travel Award}{AccessComputing, University of Washington}{Seattle, WA}{Mar. 2017}{\begin{cvitems}
\item Sponsored by The National Science Foundation (NSF).
\end{cvitems}}
    \cventry{Summer Tuition Assistance Funding}{College of Education}{University Park, PA}{2017}{}\vspace{-4.0mm}
    \cventry{Graduate Student Travel Grant}{College of Education}{University Park, PA}{Aug. 2016 - Present}{}\vspace{-4.0mm}
    \cventry{Graduate Assistantship}{Teaching and Learning with Technology}{University Park, PA}{Aug. 2016 - Present}{}\vspace{-4.0mm}
    \cventry{Outstanding Academic Award}{Hyomyoung Scholarship}{Seoul, South Korea}{2014 - 2019}{}\vspace{-4.0mm}
    \cventry{All Nations Church Graduate Scholarship}{ANC Scholarship Foundation}{Lake View Terrace, CA}{2016}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{service}{%
\section{Service}\label{service}}

\begin{cventries}
    \cventry{Search Committee for Director/Assistant Dean, Diversity, Equity, Inclusion, and Accessibility (DEIA)}{School of Information Sciences at the University of Illinois at Urbana-Champaign}{Champaign, IL}{April 2022 - Present}{}\vspace{-4.0mm}
    \cventry{Diversity Committee}{School of Information Sciences at the University of Illinois at Urbana-Champaign}{Champaign, IL}{Sep. 2021 - Apr. 2022}{}\vspace{-4.0mm}
    \cventry{Program Committee Member}{International Web for All Conference (W4A) 2022}{Virtual}{Dec. 2021 - Feb. 2022}{}\vspace{-4.0mm}
    \cventry{Accessibility Chair}{15th International Conference on Educational Data Mining}{Durham}{Oct. 2021 - Jul. 2022}{}\vspace{-4.0mm}
    \cventry{Journal Reviewer}{Special issue on ethnography and learning design}{TechTrends}{Sep. 2021}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The Network of Academic Programs in the Learning Sciences (NAPLeS)}{International Society of the Learning Sciences}{2020}{\begin{cvitems}
\item Reviewed abstracts on equity and disability.
\end{cvitems}}
    \cventry{College of Education Technology Committee}{The Pennsylvania State University}{University Park, PA}{Aug. 2019 - May. 2020}{\begin{cvitems}
\item Worked as a student committee member to support understanding of educational technology for College of Education.
\end{cvitems}}
    \cventry{Libraries' Accessibility Student Advisory Group}{The Pennsylvania State University}{University Park, PA}{Aug. 2019 - May. 2020}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The 14th International Conference of the Learning Sciences (ICLS)}{Nashville, TN}{2019}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The ACM CHI Conference on Human Factors in Computing Systems (CHI 2020, 2021)}{Honolulu, HI, Yokohama, Japan}{2019, 2020}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The 1st International Conference on Quantitative Ethnography (ICQE)}{Madison, WI}{2019}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The 3rd Learning Sciences Graduate Student Conference (LSGSC)}{Nashville, TN}{2018}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The 2nd Learning Sciences Graduate Student Conference (LSGSC)}{Bloomington, IN}{2017}{}\vspace{-4.0mm}
    \cventry{Funding Reviewer}{Center for Online Innovation in Learning (COIL), The Pennsylvania State University}{University Park, PA}{2016}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{current-memberships}{%
\section{Current Memberships}\label{current-memberships}}

\begin{itemize}
\tightlist
\item
  International Society of the Learning Sciences (ISLS)
\item
  Association for Computing Machinery (ACM)
\item
  American Statistical Association (ASA)
\item
  International Society for Quantitative Ethnography (ISQE)
\item
  International Association of Accessibility Professionals (IAAP)
\item
  International Educational Data Mining Society (IEDMS)
\end{itemize}


\label{LastPage}~
\end{document}
